\subsection{Branching Tree}
\songinfo{Fool's Garden -- Lemon Tree}{Dominik Schreiber}

I'm \chord{Am}sitting here in a \chord{Em}boring room \\
The \chord{Am}program must compile until to\chord{Em}morrow noon \\
I'm \chord{Am}wasting my time, looking \chord{Em}for a bug \\
For \chord{Am}hours and hours I am \chord{Em}trying my luck \\
But no\chord{Dm}thing ever happens \chord{Em}- and I wo\chord{Am}nder. \chord{Em \ \ Am} \\

My partner tells me, \glqq Everything's fine, \\
I fixed that problem on my branch for quite some time \\
Just fetch and merge, stage and commit \\
and don't forget to push -- that should be it\grqq \\
But nothing ever happens -- and I wonder. \\

\refrain{
	I \chord{C}wonder how, I \chord{G}wonder why, \chord{Am}Git does seem so easy for that \chord{Em}other guy \\
	but all\chord{Dm} that I can see\chord{G} is just the giant \chord{C}branching tree. \chord{G} \\
	I \chord{C}pull and push \chord{G}every time, still \chord{Am}merging conflicts haunt me every \chord{Em}second line \\
	and all\chord{Dm} that I can \chord{D}see is just that giant \chord{G}branching tree.}

Sing, \chord{Am}Git  \\
\chord{Em} Gididi di \chord{Am}Gidi-git \\
\chord{Em} Gididi di di \chord{Dm}Gidi git \\
\chord{Em} I can’t commit\chord{Am}. \ \ \ \ \chord{Em\ \ Am} \\

\pagebreak

I’m sitting here, still no success \\
I’m understanding less and less \\
A dirty worktree? What is that? \\
My eyes are heavy, I wish for my bed \\
While nothing ever happens and I wonder \\

\chord{E} Compilation \chord{Am}is so far away \\
\chord{G} Compilation -- \chord{C}I start thinking \chord{E} I just should start to pray \\

My \chord{Am}IDE de\chord{Em}synchronized \\
My \chord{Am}commands still not \chord{Em}recognized \\
And \chord{Dm}nothing ever happens \chord{Em}- and I won\chord{Am}der. \chord{Em \ \ Am}  \\

\refrain{
	I wonder how, I wonder why -- Git does seem so easy for that other guy \\
	but all that I can see is just the giant branching tree. \\
	I pull and push every time, still merging conflicts haunt me every second line \\
	and all that I can see is just that giant branching tree. \\
	And I wonder, wonder \\
	
	I  \chord{C}wonder how, I \chord{G}wonder why \\
	\chord{Am}Someone told me Git was easy \chord{Em}- What a lie! \\
	And I\chord{Dm} can’t even see\chord{G} \\
	And I\chord{F} can’t even see\chord{G} \\
	And I\chord{F} can’t even see\chord{G} \\
	The branching tree \chord{C}anymore.}

\pagebreak
